Testing and Isolation Efficacy:\\Insights from a Simple Epidemic Model \thanks{Grants or other notes about the article that should go on the front page should be placed here. General acknowledgments should be placed at the end of the article.}

### 2021-07-21 cover.tex
revised first paragraph

We are pleased to submit an original research article entitled
``Testing and Isolation Efficacy: Insights from a Simple Epidemic Model'' for your consideration for publication in \journalname{}. This study specifically aligns with the aims of \journalname{} to publish research related to the social determinants of health and adds new insight into the evolving COVID-19 pandemic.

>>>>

We are pleased to submit an original research article entitled
``Testing and Isolation Efficacy: Insights from a Simple Epidemic
Model'' for your consideration for publication in \journalname{}.  Our
study provides new insights into the evolving COVID-19 pandemic, and
more generally to epidemic dynamics in the context of testing.
